Preliminary Draft

### 2021-07-30 article/draft.tex
code for figures harmonized for Tw and Yt + new figures linked to the tex

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.34]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

%\smallskip
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.26]{../figure/Tony_Heller_videos_yt.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.26]{../figure/Tony_Heller_views_yt.png}
		%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Right Panel: accumulated view counts for videos uploaded by the same YouTube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
	%\end{multicols}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	%\end{multicols}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Data collected via the Twitter API v2 on June $16$, 2021.   }
\label{fig4}
\end{figure}

>>>>

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/lifesite_domain.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

%\smallskip
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.27]{../figure/Tony_Heller_videos_yt.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.27]{../figure/Tony_Heller_views_yt.png}
		%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Right Panel: accumulated view counts for videos uploaded by the same YouTube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_2.png} 
	%\end{multicols}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
	%\end{multicols}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on July $30$, 2021.   }
\label{fig4}
\end{figure}
